---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jugglr

<!-- badges: start -->
<!-- badges: end -->

**jugglr** is a package to validate and visualise juggling patterns. 
The `siteswap()` function takes a sequence written in siteswap notation and creates an S7 object with class `Siteswap` and a child class for the type of siteswap, e.g. vanillaSiteswap.

At present, only vanilla siteswap is implemented.
I plan to support synchronous and multiplex siteswap in the near future,
and passing siteswap after that.

## Installation

You can install the development version of jugglr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("EllaKaye/jugglr")
```

## Siteswap

Once a Siteswap object is created, it's print method will display information about the sequence,
such as whether it is a valid juggling pattern and, if so, how many props it uses.

```{r example}
library(jugglr)
# A valid juggling pattern
ss423 <- siteswap("423")
ss423
```


```{r}
# A pattern that cannot be juggled
ss21 <- siteswap("21")
ss21
```

## Visualising the patterns

There are three ways of visualising the siteswap patterns:

- A timeline plot, which shows the throws by beat
- A ladder diagram, which shows the throws by beat and hand
- An animation (only if the pattern is valid)

### Plots

These functions take `Siteswap` objects as their argument (currently only `vanillaSiteswap`). They return ggplot2 plots, so can be further customised.

```{r}
palette <- c("#D4006A", "#00D46A", "#006AD4")
timeline(ss423) +
  ggplot2::scale_color_manual(values = palette)
```

```{r}
ladder(ss423) +
  ggplot2::scale_color_manual(values = palette)
```

These plots are also useful for understand why non-valid sequences are not jugglable.
We can see, for example, where two props  would need to be caught at the same time 
(which is not permissible in vanilla siteswap).
Because each prop is shown in a different colour, we can see where balls are disappearing or needing suddenly to appear.

```{r}
timeline(ss21)
```

```{r}
ladder(ss21)
```

### Animation

**jugglr** provides a wrapper to the [JugglingLab GIF server](https://jugglinglab.org/html/animinfo.html).
Unlike the plotting functions, the main argument is any *valid* siteswap sequence as a string.

If called in Positron or RStudio, `animate()` will show the animation in the Viewer pane, 
otherwise in the browser. If a `path` argument is supplied, the animation will be saved to that location instead.
Note that it can take several seconds for the animation to render.

For embedding in RMarkdown or quarto documents, there is a wrapper, `animate_markdown()`, which calls `knitr::include_graphics()`, and display options can be set as chunk arguments (e.g. for the output below, `out.width="40%")`:

```{r, out.width="40%"}
animate_markdown("423", "man/figures/423-animation.gif", colors = palette)
```

